{\it Maxwell's Silver Hammer:}\\ On pulsed microwave acoustic resonant viral inactivation

### 2021-01-28 documents/acknowledgement.tex
why's fdtd broken?
Coplanar exposure cell working
Building the thing
Brillouin cleanups

@@

Chiefly among the enablers are of course my parents, Doris and Brian, without whom this work would have been done by someone else, and who also supported this work financially.

@@

>>>>

Special thanks to my parents, Doris and Brian, without whom this work would have been accomplished by someone else, and whose extraordinary support made this paper possible.

@@

@@

Greenland for patience

James Hawthorne for Autoleveller

Chengxiang Li and the team of who appear to have spent a decade iterating the Marx avalanche generator we use in this paper. It is an excellent, very high performance design.

### 2021-01-28 documents/brillouin_pulse_math.tex
Brillouin cleanups

@@

These are fascinating structures which arise as a result of two aspects (Albanese 
\cite{Shortrisetime1989}):

\begin{itemize}
	\item The highly dispersive nature of tissue, which causes a peculiar distortion of short pulses,
	\item The variation in loss (the imaginary part of the complex permittivity) and penetration depth versus frequency. 
\end{itemize}

@@

@@

While it is clearly possible to produce this abnormal penetration (any sharp edge suffices), it was not obvious to us that a waveform 
could be constructed that would be an effective driver for the normal modes in question. 
Oughston ; if the pulses are too close together, they distort the precursor thus formed.

@@

Unfortunately, despite NLTLs producing strong wideband components, in cursory simulations they do 
not appear to satisfy the requirements for Brillouin pulses. Our working hypothesis is that this is 
because of destructive interference from the falling edge that immediately follows; but this is 
mere speculation.
\begin{autem}
	This should be replicated.
\end{autem}

@@

\pagebreak
A qualitative statement of the problem:

@@

@@

Macke \cite{Simple2012} have come up with a number of other analytic dispersion representations for various signals, such as chirped gaussian pulses.

@@

The most promising analytical technique that we explored was essentially equivalent to Zhu, Hum, 
Costas formulation in \cite{Microwave2012b}, previously discussed by Pozar \cite{Waveform2003}, 
This is based on a lagrange multiplier technique and variational 
calculus\cite{Methods1989} \footnotetext{Based on personal communication with Professor Costas Sarris}.

@@

Pulse energy, rather than peak field, is not obviously the ideal constraint for this problem; however, it is the one most compatible with lagrange multiplier techniques.

Tufts \cite{Optimum1964}

The Euler-Lagrange equation is usually brought up in the case of the Brachistochrone problem, or 
the Principle of Least Action (see Feynman lectures). In these types of problems, it appears that 
the path of integration through space from endpoints a to b is replaced with the whole frequency 
domain from -$\infty$ to +$\infty$.

Search terms: "first variation", gateaux derivative,

@@

Numerically solving optimal control problems using CG was noted by Lasdon \cite{conjugate1967} and 
revisited by Kek \cite{Conjugate}. They reduce the computational workload by first computing the 
gradient function by hand.

@@

>>>>

\pagebreak
\section{Dispersion Timothy and the Brillouin Precursors}

Uzunoglu \cite{Theoretical2020} mention a handy way to circumvent this lossy-flesh problem: the Brillouin and Sommerfeld precursors\footnotemark, and pulse or wavepacket dispersion in tissues in general.\footnotemark

\footnotetext{
	Sincere thanks go to the legendary Kurt Oughstun for taking the time to reply to our emails.
}

\footnotetext{"precursor" is perhaps a misnomer when single pulses are used rather than trapezoidally-modulated tones - Oughston and Najafabadi both call these \textit{Brillouin pulses}.\\ \cite{Optimal2015} \cite{Optimal2017} \cite{Heat2010}.}

@@

These are fascinating structures somewhat similar to solitons, which arise as a result of an interplay between two aspects (Albanese 
\cite{Shortrisetime1989}):

\begin{itemize}
	\item The highly dispersive nature of tissue, which causes a peculiar distortion of pulses with broadband spectral content,
	\item The variation in loss (the imaginary part of the complex permittivity and the penetration depth) versus frequency. 
\end{itemize}

@@

The aspect that makes the precursors useful is that they sidestep Bragg's Law decay, with an amplitude that decays as $1/\sqrt{z}$ rather than $e^{-z}$. Note that Bragg's law is still strictly obeyed in the frequency domain (excepting second-order "bleaching" (Lukofsky \cite{Can}) or induced transparency-like (\cite{Electromagnetically1997}) effects).

@@

While it is clearly possible to produce this abnormal penetration (any sharp edge sufficiently distant from  suffices to produce a dispersive pulse), it was not obvious to us that a waveform 
could be constructed that would be an effective driver for the normal modes in question. 
Oughston ; if the pulses are too close together, they interfere as they propagate and distort the precursor thus formed.

For instance, despite the waveform from nonlinear transmission lines producing strong wideband components, in cursory simulations they did not appear to satisfy the requirements for Brillouin pulses\wikinote{dubious-discuss}\wikinote{citation-needed}. Our working hypothesis is that this is because of destructive interference from the falling edge that immediately follows; but this is mere speculation.\wikinote{dubious-discuss}

@@

@@

\pagebreak
A qualitative statement of the problem we were trying to solve (which may not be correct, especially if Q turns out to be < 1):

@@

Macke \cite{Simple2012} have come up with a number of analytic dispersion representations for various signals, such as chirped gaussian pulses; however, as it turns out, it was important that we not constrain ourselves to parameterized shapes.

@@

@@

The most promising analytical technique that we explored was a slight modification of a formulation for optimal-energy pulses, largely supplied by Prof. Costas Sarris in a yet-unpublished personal communication, based on Zhu, Hum, Costas formulation in \cite{Microwave2012b}, previously discussed by Pozar \cite{Waveform2003}.

This is based on lagrange multipliers and 'functional' or 'variational' calculus\cite{Methods1989}.

Here, rather than taking the derivative with respect to a small change in a variable, we take the derivative with respect to a small change in the function itself - a very useful technique (that the author was not aware of) which imposes little to no limitation on the form of the solution. For some intuition, the definition of the first variation and the Gateaux derivative may be of some use.

The Euler-Lagrange equation is usually brought up in the case of the Brachistochrone problem, or 
the Principle of Least Action \footnote{For background, see The Feynman Lectures, vol II chapter 19}. In these types of problems, it appears that the path of integration through space from endpoints a to b can be replaced with the whole frequency domain from -$\infty$ to +$\infty$.

@@

This lagrange multiplier technique has, however, a fundamental limitation (noted by Tufts \cite{Optimum1964}): for reasons that the author does not comprehend, only the pulse energy can be used as a constraint, rather than the value of the peak field. This seems to turn out to be of some importance.

@@

Numerically solving optimal control problems using conjugate-gradient was noted by Lasdon \cite{conjugate1967} and 
revisited by Kek \cite{Conjugate}. They reduce the computational workload by first computing the 
gradient function by hand.

@@

Of course, 10x attenuation at 1 MV/m still takes us outside. However, the loss that makes phased-array near-field focusing systems impractical at baseband is no longer a concern. A dispersive phased array with more than 10 elements may allow the complete elimination of attenuation without exceeding the limit field at any point in the body.

### 2021-01-28 documents/charge.tex
Brillouin cleanups

>>>>

Poisson-Boltzmann family of equations is an extension of standard Laplace and Poisson potentials to solutions containing ions.

Most situations solve this in equilibrium. However, we are specifically designing the pulse to be so short that ion equilibriation effects cannot occur.

First the Poisson-Boltzmann equation is run to determine the screened charge density.

$$
